High performance computing for global optimization problems

### 2018-05-15 2018/ITNT/ITNT2018.tex
Extended abstract

\documentclass[a4paper]{locconf}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\title{High performance computing for global optimization problems}

@@

@@

Computational experiments were carried out on a high-performance cluster of 
Lobachevsky State University of Nizhny Novgorod. The cluster node included 
two Intel Sandy Bridge E5-2660 2.2 GHz CPUs, 64 Gb RAM, and three NVIDIA 
Kepler K20Õ GPUs (2688 CUDA cores, 6 Gb GDDR5). 
The results of experiments demonstrate that the parallel index algorithm combined with the nested optimization scheme provides a good speedup on the considered problem class.

@@

\bibitem{Strongin2000}
Strongin, R.G. Global optimization with non-convex constraints. Sequential 
and parallel algorithms. / R.G. Strongin, Ya.D.  Sergeyev --- Dordrecht: 
Kluwer Academic Publishers, 2000. --- 704 p.

\bibitem{Strongin2013}
Strongin, R.G. Parallel computing in global optimization problems / R.G. 
Strongin, V.P. Gergel, V.A. Grishagin, K.A. Barkalov --- Moscow: Publishing 
of the Moscow State University, 2013. --- 280 p. --- (in Russian).

\bibitem{Globalizer}
Sysoyev, A.V. Globalizer -- A parallel software system for solving global optimization problems / A.V. Sysoyev, K.A. Barkalov, V.V. Sovrasov, I.G. Lebedev, V.P. Gergel // Lecture Notes in Computer Science. --- 2017. --- Vol. 10421. --- P. 492--499.

\bibitem{Jones}
Jones, D.R. The DIRECT global optimization algorithm / In: Floudas, C. A., 
Pardalos, P. M. (eds.) The Encyclopedia of Optimization, Second Edition. --- 
Heidelberg: Springer, 2009. --- P. 725--735.

\bibitem{Zilinskas}
Paulavi\v{c}ius, R. Parallel branch and bound for global optimization with 
combination of Lipschitz bounds / R. Paulavi\v{c}ius, J. \v{Z}ilinskas, A. 
Grothey // Optimization Methods \& Software. --- 2011. --- Vol. 26(3). --- P. 
487--498.

\bibitem{Evtushenko2009}
Evtushenko, Yu.G. Parallel global optimization of functions of several 
variables / Yu.G. Evtushenko, V.U. Malkova, A.A. Stanevichyus // 
Computational Mathematics and Mathematical Physics. --- 2009. --- Vol. 49 
(2). --- P. 246--260.

\bibitem{Evtushenko2014}
Evtushenko, Yu.G. Method of non-uniform coverages to solve the multicriteria optimization problems with guaranteed accuracy / Yu.G. Evtushenko, M. A. Posypkin // Automation and Remote Control. --- 2014. --- Vol. 75(6). --- P. 1025--1040.

\bibitem{Strongin2017}
Barkalov, K.A. Test problems for parallel algorithms of constrained global optimization / K.A. Barkalov, R.G. Strongin // Lecture Notes in Computer Science. --- 2017. --- Vol. 10556. --- P. 18--33.

\bibitem{Sysoyev}
Sysoyev, A.V. MPI implementation of dimension reduction multilevel scheme for 
parallel solving the global optimization problems / A.V. Sysoyev, K.A. 
Barkalov, V.P. Gergel, I.G. Lebedev // Russian Supercomputing Days: 
Proceedings of the International Scientific Conference. --- Moscow: 
Publishing of the Moscow State University, 2015. --- P. 61--68.

\bibitem{BarkalovLebedev}
Barkalov, K.A. Solving global optimization problems on GPU / K.A. Barkalov, 
I.G. Lebedev // Russian Supercomputing Days: Proceedings of the international 
conference. --- Moscow: Publishing of the Moscow State University, 2016. --- 
P. 640--650.

\bibitem{BarkalovGergel}
Barkalov, K. Parallel global optimization on GPU / K. Barkalov K., V. Gergel 
// Journal of Global Optimization. --- 2016. --- Vol. 66(1). --- P. 3--20.

\bibitem{BarkalovGergelLebedev}
Barkalov, K. Use of Xeon Phi Coprocessor for Solving Global Optimization 
Problems / K. Barkalov, V. Gergel, I. Lebedev //  Lecture Notes in Computer 
Science. --- 2015. --- Vol. 9251. --- P. 307--318.

\bibitem{Gergel2017}
Gergel, V. An Approach for Generating Test Problems of Constrained Global 
Optimization / V. Gergel // Lecture Notes in Computer Science. --- 2017. --- 
Vol. 10556. --- P. 314--319.

\bibitem{Gergel2016}
Gergel, V. Adaptive nested optimization scheme for multidimensional global 
search / V. Gergel, V. Grishagin, A. Gergel // Journal of Global 
Optimization. --- 2016. --- Vol. 66(1). --- P. 35--51.

\bibitem{Sergeyev2015}
Sergeyev, Y.D. (2015) A deterministic global optimization using smooth diagonal auxiliary functions / Y.D. Sergeyev, D.E. Kvasov // Communications in Nonlinear Science and Numerical Simulation. --- 2015. --- Vol. 21 (1-3). --- P. 99--111.

>>>>

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\title{High performance computing for global optimization problems}

@@

\ead{konstantin.barkalov@itmm.unn.ru}

@@

Computational experiments were carried out on a high-performance cluster of 
Lobachevsky State University of Nizhny Novgorod. The cluster node included 
two Intel Sandy Bridge E5-2660 2.2 GHz CPUs, 64 Gb RAM, and three NVIDIA 
Kepler K20 GPUs (2688 CUDA cores, 6 Gb GDDR5). 
The results of experiments demonstrate that the parallel index algorithm combined with the nested optimization scheme provides a good speedup on the considered problem class.

@@

\bibitem{Strongin2000}
Strongin R G and Sergeyev Ya D 2000 \textit{Global Optimization with Non-Convex Constraints. Sequential 
and Parallel Algorithms} (Dordrecht: Kluwer Academic Publishers)

\bibitem{Strongin2013}
Strongin R G, Gergel V P, Grishagin V A and Barkalov K A 2013  \textit{Parallel Computing in Global Optimization Problems} (Moscow: Moscow State University Press) (in Russian).

\bibitem{Globalizer}
Sysoyev A V, Barkalov K A, Sovrasov V V, Lebedev I G and Gergel V P 2017 \textit{Lecture Notes in Computer Science} \textbf{10421} 492--99

\bibitem{Jones}
Floudas C A and Pardalos P M 2009 \textit{The Encyclopedia of Optimization } (Heidelberg: Springer) p 725--35

\bibitem{Zilinskas}
Paulavi\v{c}ius R, \v{Z}ilinskas J and Grothey A 2011 \textit{Optim. Meth. Soft.} \textbf{26(3)} 487--98

\bibitem{Evtushenko2009}
Evtushenko Yu G, Malkova V U and Stanevichyus A A 2009 \textit{Comput. Math. Math. Phys.} \textbf{49(2)} 246--60.

\bibitem{Evtushenko2014}
Evtushenko Yu G and Posypkin M A 2014 \textit{Autom. Remote Control} \textbf{75(6)} 1025--40

\bibitem{Strongin2017}
Barkalov K A and Strongin R G 2017 \textit{Lecture Notes in Computer Science} \textit{10556} 18--33

\bibitem{Sysoyev}
Sysoyev A V, Barkalov K A, Gergel V P and Lebedev I G 2015 \textit{CEUR Workshop Proceedings} \textbf{1482} 61--68

\bibitem{BarkalovLebedev}
Barkalov K A and Lebedev I G 2016 \textit{Communications in Computer and Information Science} \textbf{687} 224--35

\bibitem{BarkalovGergel}
Barkalov K and Gergel V 2016 \textit{J. Glob. Optim.} \textbf{66(1)} 3--20

\bibitem{BarkalovGergelLebedev}
Barkalov K, Gergel V, Lebedev I 2015 \textit{Lecture Notes in Computer Science} \textbf{9251} 307--18

\bibitem{Gergel2017}
Gergel V 2017 \textit{Lecture Notes in Computer Science} \textbf{10556} 314--19

\bibitem{Gergel2016}
Gergel V, Grishagin V and Gergel A 2016 \textit{J. Glob. Optim.} \textbf{66(1)} 35--51

\bibitem{Sergeyev2015}
Sergeyev Y D and Kvasov D E 2015 \textit{Commun. Nonlinear Sci. Numer. Simul.} \textbf{21(1-3)} 99--111
